DATA 624 Homework 6

### 2020-03-14 DATA624/HW6.Rmd
More work on HW6

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(kableExtra)
library(gridExtra)
library(readxl)
options(scipen=999)
```

@@

Figure 8.31: Left: ACF for a white noise series of 36 numbers. Middle: ACF for a white noise series of 360 numbers. Right: ACF for a white noise series of 1,000 numbers.

@@

@@

@@

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(kableExtra)
library(gridExtra)
library(readxl)
library(urca)
options(scipen=999)
```

@@

**The ACF bands become narrower as the number of numbers increase.   There is no discernable pattern in the bars of the ACF charts and the bars are within the bands, which indicates the data are white noise.**

@@

**It's related to the law of large numbers.  As the number of observations increase, the number of large outliers from the mean decreases.  We are more certain that a large observation is really an outlier with more data.**

@@

```{r}
ggtsplot <- function(ts, title){
  # A ggplot2 version of tsdisplay(df)
  # Args:
  #    ts (Time-Series): The time series we want to plot
  #    title (str): The title of the graph
  grid.arrange( 
    autoplot(ts) +
      ggtitle(title) +
      theme(axis.title = element_blank()),
    grid.arrange(
      ggAcf(ts) + 
        ggtitle(element_blank()), 
      ggPacf(ts) + 
        ggtitle(element_blank()), ncol = 2), nrow = 2)
}

ggtsplot(ibmclose, "IBM Closing Stock Price")
```

**Time series with trends or with seasonality are not stationary.  It is clear from the top plot that there is a trend in IBM's stock price.  The ACF will drop to zero quickly for a stationary time series.  This ACF does not have that property.  The gradual decrease is a tell that it is not stationary.  The first PACF is almost one which is another sign that the data is not stationary.**

@@

```{r}
ggtsplot(diff(usnetelec, 1), "Differenced US Net Electricity Generation (lag=1)")
```

```{r}
#ur.kpss(diff(usnetelec, 1)) 
#Box.test(diff(usnetelec, 1), lag = 1)
usnetelec %>% diff() %>% ur.kpss() %>% summary()
```

@@

```{r}
ggtsdisplay(diff(usgdp), "US GDP")
```
